Characterization of gaps in directly bonded Si compound optics

### 2014-02-18 AO_bondedSi.tex
lots of good additions to results

\subsection{Spectra of pucks with known gap sizes}
Figures \ref{1} to \ref{2} show examples of the predicted and measured IR spectra.  Figure \ref{VS21specm1} shows an example spectrum in which the measurement is consistent with the prediction for a gap with the known conditions.  Meanwhile, Figure \ref{VS21specf1} shows a spectrum in which the measurement marginally exceeds the prediction (by about $\sim 2 \sigma$).  Other parts show less consistency with the prediction.  A complete description of the diversity of the measured spectra requires an appeal to optical phenomena beyond the scope of this paper.  Briefly we classify the diversity of measurements into the categories laid out in the table below.

@@

>>>>

\subsection{Spectra of pucks with known gap sizes}
Figures \ref{VS21specm1} to \ref{VS21specf1} show examples of the predicted and measured IR spectra.  Figure \ref{VS21specm1} shows an example spectrum in which the measurement is consistent with the prediction for a gap with the known conditions.  Meanwhile, Figure \ref{VS21specf1} shows a spectrum in which the measurement marginally exceeds the prediction (by about $\sim 2 \sigma$).  Other parts show less consistency with the prediction.  A complete description of the diversity of the measured spectra requires an appeal to optical phenomena beyond the scope of this paper.  Briefly we classify the diversity of measurements into the categories laid out in the table below.

@@

A key result of this work is to show that gaps of known dimensions are recovered in our spectroscopy.  The cases in which predicted spectroscopy differs from measurement are due to either a bona-fide detection of a gap above and beyond the implanted gap, or some measurement artifacts.  In the next section we address mitigation of artifacts.

\subsection{Mitigation of measurement artifacts}
The principle artifacts and their interpretation are listed in table \ref{1}.  We mitigated the artifacts in the following ways.  For the Sharpie marker behaving as an anti-reflection (AR) coating, we simply removed the sharpie with IPA.  We have mostly been able to rule out wavelength-dependent diffraction from the mesh pattern as a measurement artifact, since the beam size is large and the angular spread of diffraction from the mesh pattern would be much smaller than the spread of the beam.  Still, to remove this concern, we moved to using the coarse mesh rather than the medium or fine meshes, when possible.  We saw no difference in the bond quality surrounding the medium or fine meshes, which is consistent with results from the literature (see the work of Mitani and collaborators from the mid 1990s).  Namely, Mitani showed that the gas pressure of bonded wafers grew as the fill factor of voids decreased.  In other words, what matters is the fill factor of voids, not their relative sizes.  Since the fine, medium, and coarse meshes had the same fill factors, we anticipate no difference in the pressure of the voids, and therefore no difference in the bonding properties.

Our sensitive measurement technique introduces a few challenges at the parts per thousand level baseline level.  Specifically, we have been ambivalent about whether or not to use the double-beam capability of the Cary5000.  We have shown that this mode reduces by a factor of 10, the random flicker attributable to lamp noise.  In practice, the double beam mode can cause some systematic problems near the portions of wavelengths near lamp and filter changes.  So of these issues might be related to polarization differences, and a way to mitigate these techniques is to follow the advice of the vendor and employ a depolarizer in the beam path.  A depolarizer strategy is critical for applications in which a non-normal incidence angle is desired.  A half-hearted attempt to measure non-normal incidence without the polarization accessory resulted in failure.  In the next section we describe our interest in non-normal incidence.

\subsection{Non-normal incidence angles}
For many applications, normal incidence performance is the quantity of interest.  The technique described here outlines an approach for measuring the gap size of bonded Si wafers at normal incidence.  In principle, from there the performance at non-normal incidence can be worked out either by simulation or calculation.  Here we briefly motivate the challenge of experiment and simulation at non-normal incidence.

Our final application that motivated this project is to make diffraction gratings on the hypotenuse of a silicon prism.  The diffraction occurs inside the silicon material and is dispersed and reflected back along its path.  This configuration is called an immersion grating.  Our group has made monolithic immersion gratings for over a decade, but challenges in processing large (30 mm thick) Si wafers motivated an approach of patterning and processing thin (1-10 mm thick) Si wafers, and then bonding them to shaped and polished prisms.  This technique has been pioneered at SRON.

The consequence of our design is a non-normal incidence interface in double pass.  In this case, the framework developed here fails to predict the spectrum of the interface loss attributable to a finite albeit small (few nm) gap.  Specifically, at large incidence angles complete internal reflection and evanescent waves will matter.  Polarization effects are important.

\subsection{Spectra of pucks with no implanted gap}
We have shown that the IR spectroscopy technique combined with the Fabry-P\'{e}rot framework provide accurate knowledge of the gap size.  In the cases where we expected no gap (i.e. perfect Si-Si bond), we have seen spectra consistent with 100\% transmission relative to a DSP Si wafer.  In other cases we have seen evidence for gaps, which is simply an indication that the bonding process introduces gaps.  In a followup paper we will describe ways to mitigate bond formation in bonded Si pucks.

\section{Conclusions}
We have shown a method for indirectly measuring the size of voids in bonded Si wafers.  The technique broadly applies to any compound Si optics measured at normal incidence.  We showed lab IR spectra with consistent predictions, and addressed ways to mitigate measurement artifacts.
